---
title: "Knowledge and Ignorance Processing is Faster than Belief Processing"
subtitle: "Analysis Report - Experiments 1-3"
author:
 - name: Smith, A. 
 - name: Peney, T.
 - name: Tidoni, E.
 - name: O'Connor, R. J.
 - name: Riggs, K.
analysis-author: Peney, T.
date: today
date-format: "YYYY-MM-DD"
lang: en-GB
format:
  html:
    embed-resources: true
    toc: true
    toc-depth: 3
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    anchor-sections: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(here)
library(gt)

here::i_am("_experiment_report.qmd")
```

```{r}
table_formatting <- function(gt_table){
    gt_table |> 
        tab_options(table.align = "left") |> 
        fmt_number(decimals = 3, drop_trailing_zeros = TRUE) |> 
        sub_small_vals(threshold = 0.001)
}
```

# Experiment 1
```{r}
results <- read_rds(here("outputs/exp1_results.rds"))
```

## Exclusions
```{r}
results$exclusions
```

## Descriptives
```{r}
results$descriptives
```

## Confirmatory Analysis
```{r}
results$anova |> 
    gt() |> tab_header(title = "Repeated Measures ANOVA") |> table_formatting()

results$ttests |> 
    gt() |> tab_header(title = "Pairwise Repeated Measures T-Tests") |> table_formatting()
```

# Experiment 2
```{r}
results <- read_rds(here("outputs/exp2_results.rds"))
```

## Exclusions
```{r}
results$exclusions
```

## Descriptives
```{r}
results$descriptives
```

## Confirmatory Analysis
```{r}
results$anova |> 
    gt() |> tab_header(title = "Repeated Measures ANOVA") |> table_formatting()

results$ttests |> 
    gt() |> tab_header(title = "Pairwise Repeated Measures T-Tests") |> table_formatting()
```

# Experiment 3
```{r}
results <- read_rds(here("outputs/exp3_results.rds"))
```

## Exclusions
```{r}
results$exclusions
```

## Descriptives
```{r}
results$descriptives
```

## Confirmatory Analysis
```{r}
results$ttests |> 
    gt() |> tab_header(title = "Pairwise Repeated Measures T-Tests") |> 
    table_formatting()
```

# Supplementary Analysis
## Experiment 2
```{r}
results <- read_rds(here("outputs/exp2_supplementary_results.rds"))
```

### Supplementary Test 1 - Reported in main text
Comparing RT between Knowledge statements that are False and Belief statements that are False. FB-Ig Scenario trials.
```{r}
results$S1$rt
results$S1$ttest |> gt() |> table_formatting()
```

### Supplementary Test 2
Comparing RT between Knowledge statements that are False and Belief statements that are True. FB-Ig Scenario trials.
```{r}
results$S2$rt
results$S2$ttest |> gt() |> table_formatting()
```

### Supplementary Test 3
Comparing RT between (a) mean RT for False K statements / mean RT for False R statements (b) mean RT for True B statements / mean RT for True R statements.
```{r}
results$S3$rt
results$S3$ttest |> gt() |> table_formatting()
```

### Supplementary Test 4
Check that the number of cubes referred to in the statement does not produce a difference in RTs. No Barrier: TB-K scenario trials only.
```{r}
results$S4$rt
results$S4$ttest |> gt() |> table_formatting()
```

# Session Info
```{r}
sessionInfo()
```